The unequal distribution of access to education and transport:

### 2016-02-11 paper.Rmd
Update references (all included now)

In spite of its simplicity, Boisjoly and El-Geneidy (2016) have found that the cumulative-opportunity measure (using a 45 minute threshold) is highly correlated with a gravity-based accessibility measure ([@handy1997measuring], [@hansen1959accessibility]), defined as:

>>>>

In spite of its simplicity, Boisjoly and El-Geneidy (2016) have found that the cumulative-opportunity measure (using a 45 minute threshold) is highly correlated with a gravity-based accessibility measure ([@handy_measuring_1997], [@hansen1959accessibility]), defined as:
